Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production,

### 2016-07-11 inst/examples/notebook.Rmd
ok

---
title: "Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828"
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: "`r Sys.Date()`"
output: 
  beamer_presentation
---

>>>>

---
title: 'Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production,
  1640-1828'
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: '`r Sys.Date()`'
output:
  word_document: default
  pdf_document: default
  html_notebook: default
---
